---
title: "Tableau Project 3"
output: html_document
---
Created by: Natasha Halfin, Evan Johnston, and Kaylyn Zvonek 

```{r, echo=TRUE}
library("ggplot2")
library("gplots")
library("bitops")
library("knitr")
library("jsonlite")
library("ggthemes")
library("RCurl")
library("reshape2")
library("tidyr")
library("dplyr")
library("grid")
```
While TopCompanies does not include every company in a state, it is interesting to view the statistics of states that are doing well within the top companies list. For instances if there are more companies from a particular state on the top 200 companies list, it would be interesting to look at how well people on average are paid within that state. 
```{r, eval = TRUE, echo=TRUE}


```


From the TopCompanies data set we found the number of companies based on state and compared it to the StateEmployment's average company payroll for that state. 
```{r, eval=TRUE, echo=TRUE}

```

From the TopCompanies data set we found the average Top 200 company's revenue based on state and compared it to the StateEmployment set's average payroll based on state. We thought it would be interesting to see if the states with more top companies paid higher. Conneticut by far the highest revenue which could be attributed to companies like GE being based there.  
```{r, eval=TRUE, echo=TRUE}

```


From the TopCompanies data set we found the average growth of each state and compared it to the StateEmployment's number of establishments by state. We thought it would be interesting to see if the states with more growth had  
```{r, eval=TRUE, echo=TRUE}

```


From the TopCompanies data set we found the number of companies based on state and compare it to the StateEmployment's employment numbers. 
```{r, eval=TRUE, echo=TRUE}

```



